---
title: ""
author: ""
date: "`r format(Sys.time(), '%B %d, %Y %H:%M')`"
output:
  html_document:
    number_sections: FALSE
    self_contained: TRUE
    toc: TRUE
    toc_float: TRUE
    css: !expr here::here("www", "web_report.css")
    editor_options:
      chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css?family=Lato&display=swap');
</style>

<link rel="stylesheet" href="//fonts.googleapis.com/css?family=Lato" />



```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = FALSE)

```

```{r setup}
options(scipen = 999)

library(tidyverse)
library(sf)
library(mapview)
library(googlesheets4)
library(janitor)
library(urbnthemes)

set_urbn_defaults(base_size = 13)
```


```{r}
gs4_deauth()


funds_df = read_sheet("https://docs.google.com/spreadsheets/d/1rboROHhryc_x7PPCwfJo6LjEkfDIAuXlmP8IHsc0CKM/edit?usp=sharing") %>% 
  arrange(desc(Total)) %>% 
  # Only keep centers with some funds donated
  filter(Total > 0)



```




# Background

Urban employees are working across centers to raise money for mutual aid organizations working in Texas that have been affected by the recent winter storms ....


# Center Totals
#### Last updated `r format(Sys.time(), '%B %d, %Y %H:%M')`


```{r}
first_place_center = funds_df %>% slice(1) %>% pull(Center)
 
title_with_first_place = paste0(first_place_center, " is in first place!")

funds_df %>% 
  mutate(Center = fct_reorder(Center, Total, .desc = FALSE)) %>% 
  ggplot(aes(y = Center, x = Total)) +
  geom_col() +
  geom_text(aes(label = scales::dollar(Total)), hjust = -0.2, size = 5, color = palette_urbn_cyan[6]) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_x_continuous(expand = expansion(add = c(0, 190))) +
  labs(y = "", title= title_with_first_place)
```


# Where is the money going?

We are aiming to donate the money to a collection of mutual aid organizations in Texas. So far these include:

 - Org 1
 - Org 2
 
 
# How to donate?


